Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
Threat model discussion

\bcp{I think we are not explicit enough about the sorts of threat situations
  we imagine we are addressing.  A canonical example (that we could spell
  out) is a developer who wants to call out to potentially buggy or
  malicious libraries.  The library code is going to be linked with the
  developer's in the same address space, but the developer wants her private
  data to be protected from both reading/exfiltrating and
  overwriting... More generally, we can talk about the fact that programmers
  use simple reasoning principles to think about their programs (e.g., local
  variables don't change across function calls), and life is better when
  these principles are actually true...}

>>>>

Consider a common scenario: a developer wants to link against an existing
code-base, which will then occupy the same address space as their own code.
But perhaps the external code is buggy, or even malicious, and contains
exploits that can be used to cause it to modify the developer's data or
exfiltrate secrets. For that matter, the developer may not be a particularly
secure programmer, and may not be able to rely on their own defensive programming
to keep their secrets safe.

The developer likely relies instead on simple reasoning principles about how
their code should work. Local variables do not change across function calls,
and the callees generally do the same thing regardless of when and where they
are called (up to a reasonable interface, such as their parameters and global
variables.) If these intuitions prove false, then the programmer will reason
incorrectly about their program and especially about its security, and
be exposed to attack.
